An indexed construction of semi-cubical types

### 2021-07-09 paper/paper.tex
[paper] Switch to amsart; clean up junk macros

\documentclass{article}

\usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
\usepackage{bookmark, titling, fontspec, xargs, multirow, polyglossia, luacode, fancyhdr, lastpage, amssymb}
\usepackage{listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell}
\usepackage[compact]{titlesec}
\usepackage[margin=0.5in]{geometry}

@@

\include{macros}

@@

% The unit type
\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}

% Definitional and extensional equality
\newcommand{\defeq}{\ensuremath{\triangleq}}
\newcommand{\eqett}{\equiv_{\mathit{ETT}}}

% Box, layer, and cube
\newcommand{\mybox}[2]{\ensuremath{\mathsf{box}_{#1}^{#2}}}
\newcommand{\mylayer}[2]{\ensuremath{\mathsf{layer}_{#1}^{#2}}}
\newcommand{\mycube}[2]{\ensuremath{\mathsf{cube}_{#1}^{#2}}}

@@

% Border
\newcommand{\border}[1]{\ensuremath{\mathsf{border}_{#1}}}

% Partials and fulls
\newcommand{\partialcubset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
\newcommand{\mycubsetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
\newcommand{\fulldownbox}[2]{\mathsf{subfullbox}_{#1}^{#2}}
\newcommand{\fulldowncube}[2]{\mathsf{subfullcube}_{#1}^{#2}}

@@

% Junk follows

\newcommand{\revimp}{\ensuremath{\leftarrow}}

\newcommand{\Type}{\ensuremath{\mathsf{Type}}}
\newcommand{\Set}{\ensuremath{\mathsf{Set}}}
\newcommand{\Prop}{\ensuremath{\mathsf{Prop}}}
\newcommand{\refl}[1]{\ensuremath{\mathsf{refl}\,{#1}}}
\newcommand{\mkmlidtype}[3]{{#1} =^{\mathrm{id}}_{#2} {#3}}
\newcommand{\mkmleqdep}[3]{{#1} =^{\mathrm{dep}}_{#2} {#3}}
\newcommand{\hrefl}[1]{\ensuremath{\mathsf{refl^{\mathrm{dep}}}\,{#1}}}
\newcommand{\mluniv}{\ensuremath{\mathsf{U}}}
\newcommand{\Jdep}[2]{\ensuremath{\mathsf{J}\;{#1}\;{#2}}}

\newcommand{\nth}[1]{{#1}^{\mbox{\scriptsize th}}}
\newcommand{\binomial}[2]{\left(\begin{array}{c}#1\\#2\end{array}\right)}

\newcommand{\wfctx}[1]{{#1}~\mathsf{ok}}

\newcommand{\mkover}[1]{\widetilde{#1}}
\newcommand{\mkoverdim}[2]{\widetilde{#2}^{#1}}
\newcommand{\mkprod}[3]{\Pi {#2}.\,{#3}}
\newcommand{\mkprodovereq}[3]{\mkover{\Pi} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkprodovereqopp}[3]{\opp{\mkover{\Pi}} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkboundedprod}[4]{\Pi {#3}\!:\!{#1}\leq{#2}.\,{#4}}
\newcommand{\mklam}[3]{\lambda^{#2}.\,{#3}}
\newcommand{\mkboundedlam}[4]{\lambda {#3}\!:\!{#1}\leq{#2}.\,{#4}}
\newcommand{\mkapp}[2]{{#1}\,{#2}}
\newcommand{\prodsort}[2]{\Pi ({#1},{#2})}

% selecting kind of treatment of sorts
\newcommand{\typeorsort}[2]{{#2}}

\newcommand{\mksigma}[3]{\Sigma {#2}.\,{#3}}
\newcommand{\mksigmaovereq}[3]{\mkover{\Sigma} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mksigmaovereqopp}[3]{\opp{\mkover{\Sigma}} {#1}\!:\!{#2}.\,{#3}}
\newcommand{\mkpair}[2]{\langle{#1},{#2}\rangle}
\newcommand{\mkfst}[1]{{#1}.1}
\newcommand{\mksnd}[1]{{#1}.2}
\newcommand{\sigsort}[2]{\Sigma ({#1},{#2})}

\newcommand{\sortsort}[1]{{\mathcal S}_{#1}}

\newcommand{\Sone}{\mathbb{S}^1}
\newcommand{\casesone}[5]
  {\mathsf{case}\;{#1}\;\mathsf{of}\;{#2}\;\Rightarrow\;{#3}\;|\;{#4}\;\Rightarrow\;{#5}\;\mathsf{end}}
\newcommand{\base}{\mathsf{base}}
\newcommand{\loopsone}{\mathsf{loop}}
\newcommand{\Sonesort}{l_{\mathbb{S}^1}}

\newcommand{\emptyctx}{\boxbox}

\newcommand{\univ}{\boxempty}
\newcommand{\typeannot}{\mathsf{type}}
\newcommand{\istype}{~\typeannot}

\newcommand{\mkeq}[3]{{#1} =_{#2} {#3}}
\newcommand{\mkhomeq}[3]{{#1} =_{#2} {#3}}
\newcommand{\mkeqovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}}
\newcommand{\mkeqovereqdim}[4]{{#2} \,\mkoverdim{#1}{=}_{#3}\, {#4}}
\newcommand{\mkeqtype}[3]{{#1} =_{\typeannot} {#3}}
\newcommand{\mkeqtypeovereq}[3]{{#1} \,\mkover{=}_{#2}\, {#3}} % case where we can write either s or refl{s}
\newcommand{\mkeqarray}[3]{\begin{array}{c}{#1}\\ =_{#2}\\ {#3}\end{array}}
\newcommand{\mkfaces}[3]{\mkeq{#1}{#2}{#3}}
\newcommand{\mkfacesarray}[3]{\mkeqarray{#1}{#2}{#3}}
\newcommand{\mkfacesover}[3]{\mkeqovereq{#1}{#2}{#3}}
\newcommand{\lameq}[2]{\lambda {#1}.{#2}}
\newcommand{\reflterm}[1]{\widehat{#1}}
\newcommand{\overreflterm}[1]{{\mkover{\reflterm{#1}}}}
\newcommand{\refltermdim}[2]{{\widehat{#2}}^{#1}}
\newcommand{\refltype}[1]{\reflterm{#1}}
\newcommand{\purerewlr}[1]{\overrightarrow{#1}}
\newcommand{\purerewrl}[1]{\overleftarrow{#1}}
\newcommand{\rewlr}[2]{\overrightarrow{#1}(#2)}
\newcommand{\rewrl}[2]{\overleftarrow{#1}(#2)}
\newcommand{\deprewlr}[1]{\raisebox{0em}{$\ulcorner$}\!#1}
\newcommand{\deprewrl}[1]{{#1}\raisebox{-0.2em}{$\!\lrcorner$}}
\newcommand{\rewlrspec}[2]{{#1}^{\rightarrow}(#2)}
\newcommand{\rewrlspec}[2]{{#1}^{\leftarrow}(#2)}
\newcommand{\rewlrrevspec}[2]{{#1}_-^{\rightarrow}(#2)}
\newcommand{\rewrlrevspec}[2]{{#1}_-^{\leftarrow}(#2)}
\newcommand{\rewlrrevspecin}[2]{{#1}_+^{\rightarrow}(#2)}
\newcommand{\rewrlrevspecin}[2]{{#1}_+^{\leftarrow}(#2)}
\newcommand{\doublerewlr}[2]{\Overrightarrow{1.4ex}{#1}({#2})}
\newcommand{\doublerewrl}[2]{\Overleftarrow{1.4ex}{#1}({#2})}
\newcommand{\mktuple}[6]{\{#3; #4; #5; #6\}_{#1,#2}}
\newcommand{\mktupleshort}[6]{\{#3; #4; #5; #6\}}
\newcommand{\opp}[1]{{#1}^{-1}}
\newcommand{\oppi}[2]{\appi{#1}{(\opp{#2}/{#2})}}

\newcommand{\weakensquarelr}[2]{{#1}_L(#2)}
\newcommand{\weakensquarerl}[2]{{#1}_R(#2)}

\newcommand{\rewlrmkeq}[4]{\mkeq{\rewlr{#1}{#2}}{#3}{#4}}

\newcommand{\appi}[2]{{#1}\;\!{#2}}
\newcommand{\appidep}[2]{{#1}_{#2}}
\newcommand{\bp}[1]{{#1}{\scriptstyle 0}}
\newcommand{\ep}[1]{{#1}{\scriptstyle 1}}
\newcommand{\bpoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{0}}}
\newcommand{\epoverdim}[2]{{#2}{\scriptstyle \mkoverdim{#1}{1}}}
\newcommand{\bpdep}[1]{{#1}_0}
\newcommand{\epdep}[1]{{#1}_1}

\newcommand{\bpsubstexpl}[2]{{#2}_{\{0/{#1}\}}}
\newcommand{\epsubstexpl}[2]{{#2}_{\{1/{#1}\}}}
\newcommand{\eqsubstexpl}[2]{{#2}_{\{\star/{#1}\}}}
\newcommand{\bpsubstexplcons}[2]{{#2}\}\{0/{#1}}
\newcommand{\epsubstexplcons}[2]{{#2}\}\{1/{#1}}
\newcommand{\eqsubstexplcons}[2]{{#2}\}\{\star/{#1}}
\newcommand{\bpsubst}[2]{{#2}{[0/{#1}]}}
\newcommand{\epsubst}[2]{{#2}{[1/{#1}]}}
\newcommand{\bpsubstctx}[3]{{#3}{[0/{#2}]}^{#1}}
\newcommand{\epsubstctx}[3]{{#3}{[1/{#2}]}^{#1}}
\newcommand{\takebpface}[2]{\partial^{#1}_0{#2}}
\newcommand{\takeepface}[2]{\partial^{#1}_1{#2}}

\newcommand{\dimvalid}[2]{{#1} \in {#2}}
\newcommand{\dimdeclare}[1]{{#1}}
\newcommand{\dimlength}[1]{|#1|_{\mathit{dim}}}
\newcommand{\dimindex}[2]{\#_{#1}{#2}}

\newcommand{\substminus}[2]{{#1}-{#2}}
\newcommand{\substminusbernardymoulin}[2]{{#1}/{#2}}

\newcommand{\N}{\mathbb{N}}
\newcommand{\expand}[2]{\mathsf{expand}(#1,#2)}

\newcommand{\metaequiv}{\cong}
\newcommand{\metaletin}[3]{\mathit{let}\;{#1}\;\defeq\;{#2}\;\mathit{in}\;{#3}}
\newcommand{\map}[2]{\mathsf{ap}\,{#1}\,{#2}}
\newcommand{\depmap}[2]{\mathsf{apd}\,{#1}\,{#2}}
\newcommand{\transport}[3]{\mathsf{transport}\,{#1}\,{#2}\,{#3}}
\newcommand{\deptransport}[3]{\mathsf{transportd}\,{#1}\,{#2}\,{#3}}
\newcommand{\swap}[1]{{#1}^{\circ}}
\newcommand{\swapbracket}[1]{({#1})^{\circ}}
\newcommand{\swaptype}[1]{{#1}^{\circ}}
\newcommand{\swapoverdim}[2]{{#2}^{\mkoverdim{#1}{\circ}}}
\newcommand{\homsquare}[1]{\mathsf{homsquare}(#1)}
\newcommand{\permute}[2]{\mathsf{permute}_{#1}(#2)}
\newcommand{\swapprodeq}[2]{\mathsf{swap}_{\Pi=}^{#1}(#2)}
\newcommand{\swapeqprod}[2]{\mathsf{swap}_{=\Pi}^{#1}(#2)}
\newcommand{\swapeqprodlr}[2]{\mathsf{swap}_{=\Pi}^{\rightarrow}({#1})(#2)}
\newcommand{\swapeqprodrl}[2]{\mathsf{swap}_{=\Pi}^{\leftarrow}({#1})(#2)}
\newcommand{\swapsigmaeq}[1]{\mathsf{swap}_{\Sigma=}(#1)}
\newcommand{\swapeqsigma}[1]{\mathsf{swap}_{=\Sigma}(#1)}

\newcommand{\bool}{\mathsf{bool}}
\newcommand{\booldeux}{\bool^2}
\newcommand{\boolexp}{\bool^{\bool}}

\newcommand{\reduce}{\;\triangleright\;}

\newcommand{\emptysubst}{\emptyctx}

\newcommand{\sortrule}{\sort{}}
\newcommand{\axrule}{\mathsf{Ax}}
\newcommand{\ctxemptyrule}{\mathsf{Ctx}_{\emptyctx}}
\newcommand{\ctxconsrule}{\mathsf{Ctx}_{\mathsf{cons}}}
\newcommand{\convrule}{\mathsf{Conv}}
\newcommand{\convconvrule}{\mathsf{Conv}-\mathsf{Conv}}
\newcommand{\univrule}{\mathsf{\univ}}
\newcommand{\convruleredright}{\reduce_R}
\newcommand{\convruleredleft}{\reduce_L}
\newcommand{\convrulerefl}{\equiv_{\mathsf{refl}}}
\newcommand{\convruletrans}{\equiv_{\mathsf{trans}}}
\newcommand{\convruleredtyperight}{\reduce_R^{\typeannot}}
\newcommand{\convruleredtypeleft}{\reduce_L^{\typeannot}}
\newcommand{\convruletyperefl}{\equiv_{\mathsf{refl}}^{\typeannot}}
\newcommand{\convruletypetrans}{\equiv_{\mathsf{trans}}^{\typeannot}}

\newcommand{\circovereq}{\;\mkover{\circ}\;}
\newcommand{\circsigma}{\circ_{\Sigma}}

\newcommand{\comprule}{R_{\mathsf{\circ}}}
\newcommand{\opprule}{R_{\mathsf{\opp}}}

\newcommand{\idleftredrule}{\mathsf{Id_L}}
\newcommand{\idrightredrule}{\mathsf{Id_R}}
\newcommand{\idoppredrule}{\mathsf{\opp{Id}}}
\newcommand{\oppoppredrule}{\mathsf{\opp{(\opp{\_})}}}
\newcommand{\assoccompredrule}{\mathsf{Assoc}}
\newcommand{\distriboppcompredrule}{\mathsf{\opp{\circ}}}
\newcommand{\squaredownredrule}{\circ_{=_{\mkover{=}}}}
\newcommand{\exchangerule}{\mathsf{Exch}}
\newcommand{\compeqovereqredrule}{\circ_{\mkover{=}}}
\newcommand{\squareprodredrule}{\circ_{=_{\mkover{\Pi}}}}

\newcommand{\depmapdef}{\mathsf{ApD}}
\newcommand{\funextpuredef}{\mathsf{LiftDim}}
\newcommand{\funextdeppuredef}{\mathsf{LiftDepDim}}
\newcommand{\funextdepdeppuredef}{\mathsf{LiftDepDim}}
\newcommand{\funextdef}{\mathsf{FunExt}}
\newcommand{\funextdepdef}{\mathsf{FunDepExt}}
\newcommand{\funext}[1]{\mathsf{funext}(#1)}
\newcommand{\funextdep}[1]{\mathsf{fundepext}(#1)}
\newcommand{\funextpure}[1]{\mathsf{liftdim}(#1)}
\newcommand{\funextdeppure}[1]{\mathsf{liftdepdim}(#1)}

\newcommand{\OMEGATT}{\omega\mathsf{TT}}

\newcommand{\emptysigma}{\bullet}
\newcommand{\itsemterm}[4]{\llbracket #4 \rrbracket^{#2;#3}_{#1}}
\newcommand{\itsemtype}[4]{\llbracket #4 \rrbracket^{#2;#3}_{#1}}
\newcommand{\semterm}[3]{\llbracket #3 \rrbracket^{#1;#2}}
\newcommand{\semtype}[3]{\llbracket #3 \rrbracket^{#1;#2}}
\newcommand{\incrstep}[3]{\mathsf{split}_{#1}{#3}(#2)}
\newcommand{\distrstep}[3]{\mathsf{distr}_{#1}{#3}(#2)}
\newcommand{\applytype}[4]{\mathsf{apptype}_{#1}^{#2}(#3,#4)}
\newcommand{\shrink}[3]{\mathsf{shrink}_{#1}\,{#2}\,#3}
\newcommand{\under}[3]{\mathsf{under}_{#1}\,{#2}\,#3}
\newcommand{\undertau}[3]{\mathsf{under}_{#1}^{#2}\,#3}
\newcommand{\proj}[3]{\pi_{#1}^{#2}\,#3}
\newcommand{\elt}[2]{\mathsf{El}_{#1}\,#2}
\newcommand{\semtypenew}[2]{| #2 |_{#1}}
\newcommand{\semnew}[2]{\llbracket #2 \rrbracket_{#1}}
\newcommand{\semctx}[2]{\llbracket #2 \rrbracket_{#1}}
\newcommand{\semlam}[5]{\mathsf{lam}_{#1}^{#2}\,#4\,(#3)\,#5}
\newcommand{\semlambis}[5]{\mathsf{lam'}_{#1}^{#2}\,#4\,(#3)\,#5}
\newcommand{\semapp}[3]{\mathsf{app}_{#1}#2\,#3}
\newcommand{\semprod}[5]{\mathsf{prod}_{#1}^{#2}\,#4\,(#3)\,#5}
\newcommand{\access}[2]{\mathsf{get}_{#1}(#2)}
\newcommand{\accesstyped}[3]{\mathsf{get}_{#1}^{#2}(#3)}
\newcommand{\lift}[1]{\mathsf{lift}\, {#1}}
\newcommand{\liftlr}[1]{\mathsf{lift}^\rightarrow\, {#1}}
\newcommand{\liftrl}[1]{\mathsf{lift}^\leftarrow\, {#1}}
\newcommand{\diag}[2]{\mathsf{diag}_{#1}(#2)}
\newcommand{\semsort}[1]{\mathsf{sort}_{#1}}
\newcommand{\reflsort}[1]{\mathsf{refl}^{\sort{}}_{#1}}
\newcommand{\mktuplenew}[6]{\{#4\,|\begin{array}{l} #5 \\ #6 \end{array}\}_{#1,#2,#3}}
\newcommand{\mktuplein}[4]{{#1}; {#2}; {#3}; {#4}}
\newcommand{\nwconn}[2]{\deprewlr{#2}_{#1}}
\newcommand{\seconn}[2]{\deprewrl{#2}_{#1}}
\newcommand{\refltermn}[3]{\mathsf{reflterm}_{#1}(#3)}
\newcommand{\refltypen}[2]{\mathsf{refltype}_{#1}(#2)}

\newcommand{\restrict}{\mathsf{restrict}}
\newcommand{\MofL}{\mathsf{underlying}}
\newcommand{\defequiv}{\mathsf{\simeq}}
\newcommand{\isequivalence}{\mathsf{isequiv}}
\newcommand{\gpdlevel}{\mathsf{gpdlevel}}
\newcommand{\regrefl}{\mathsf{regrefl}}

\newcommand{\heteroname}{het}

\newcommand{\informalcube}{\mathsf{cube}}
\newcommand{\informalcubeover}{\mathsf{cube}}

\newcommand{\pboxname}{box}
\newcommand{\pBoxname}{Box}

\newcommand{\myheterobox}[2]{\mathsf{{\heteroname}box}_{#1}^{#2}}
\newcommand{\myheterolayer}[2]{\mathsf{{\heteroname}layer}_{#1}^{#2}}
\newcommand{\myheterocube}[2]{\mathsf{{\heteroname}cube}_{#1}^{#2}}
\newcommand{\myheteroboxtype}[2]{\mathsf{Box}_{#1}^{#2}}
\newcommand{\myheterolayertype}[2]{\mathsf{Layer}_{#1}^{#2}}
\newcommand{\myheterocubetype}[2]{\mathsf{Cube}_{#1}^{#2}}

\newcommand{\myfulldepheterobox}[3]{\mathsf{fulldepBox}_{#1}^{#2,#3}}
\newcommand{\mydepheterobox}[3]{\mathsf{depBox}_{#1}^{#2,#3}}
\newcommand{\mydepheterolayer}[3]{\mathsf{depLayer}_{#1}^{#2,#3}}
\newcommand{\mydepheterocube}[3]{\mathsf{depCube}_{#1}^{#2,#3}}
\newcommand{\liftfulldepheterobox}[3]{\mathsf{liftfullBox}_{#1}^{#2,#3}}
\newcommand{\liftdepheterobox}[3]{\mathsf{liftBox}_{#1}^{#2,#3}}
\newcommand{\liftdepheterolayer}[3]{\mathsf{liftLayer}_{#1}^{#2,#3}}
\newcommand{\liftdepheterocube}[3]{\mathsf{liftCube}_{#1}^{#2,#3}}

\newcommand{\expandheterocube}[2]{\mathsf{expandCube}_{#1}^{#2}}
\newcommand{\expandheterolayer}[2]{\mathsf{expandLayer}_{#1}^{#2}}
\newcommand{\expanddownbox}[2]{\mathsf{expandsubbox}_{#1}^{#2}}
\newcommand{\expanddownlayer}[2]{\mathsf{expandsublayer}_{#1}^{#2}}
\newcommand{\expanddowncube}[2]{\mathsf{expandsubcube}_{#1}^{#2}}

\newcommand{\depdownbox}[2]{\mathsf{depsubbox}_{#1}^{#2}}
\newcommand{\depdownlayer}[2]{\mathsf{depsublayer}_{#1}^{#2}}
\newcommand{\depdowncube}[2]{\mathsf{depsubcube}_{#1}^{#2}}
\newcommand{\depdownboxbis}[2]{\mathsf{depsubliftbox}_{#1}^{#2}}
\newcommand{\depdownlayerbis}[2]{\mathsf{depsubliftlayer}_{#1}^{#2}}
\newcommand{\depdowncubebis}[2]{\mathsf{depsubliftcube}_{#1}^{#2}}
\newcommand{\depdownboxter}[2]{\mathsf{depsubliftbox'}_{#1}^{#2}}
\newcommand{\depdownlayerter}[2]{\mathsf{depsubliftlayer'}_{#1}^{#2}}
\newcommand{\depdowncubeter}[2]{\mathsf{depsubliftcube'}_{#1}^{#2}}

\newcommand{\depcohbox}[2]{\mathsf{depcohbox}_{#1}^{#2}}
\newcommand{\depcohlayer}[2]{\mathsf{depcohlayer}_{#1}^{#2}}
\newcommand{\depcohcube}[2]{\mathsf{depcohcube}_{#1}^{#2}}
\newcommand{\depcohboxbis}[2]{\mathsf{depcohliftbox}_{#1}^{#2}}
\newcommand{\depcohlayerbis}[2]{\mathsf{depcohliftlayer}_{#1}^{#2}}
\newcommand{\depcohcubebis}[2]{\mathsf{depcohliftcube}_{#1}^{#2}}
\newcommand{\depcohboxter}[2]{\mathsf{depcohliftbox'}_{#1}^{#2}}
\newcommand{\depcohlayerter}[2]{\mathsf{depcohliftlayer'}_{#1}^{#2}}
\newcommand{\depcohcubeter}[2]{\mathsf{depcohliftcube'}_{#1}^{#2}}

\newcommand{\univfullcube}[2]{\mathsf{UnivfullCube}_{#1}^{#2}}
\newcommand{\univfullbox}[2]{\mathsf{UnivfullBox}_{#1}^{#2}}
\newcommand{\univbox}[2]{\mathsf{UnivBox}_{#1}^{#2}}
\newcommand{\univlayer}[2]{\mathsf{UnivLayer}_{#1}^{#2}}
\newcommand{\univcube}[2]{\mathsf{UnivCube}_{#1}^{#2}}
\newcommand{\univfiller}[2]{\mathsf{UnivFiller}_{#1}^{#2}}
\newcommand{\cubeofuniv}[2]{\mathsf{cubeofuniv}_{#1}^{#2}}
\newcommand{\extend}[2]{\mathsf{extendcube}_{#1}^{#2}}

\newcommand{\powersetfullcube}[2]{\mathsf{powersetfullCube}_{#1}^{#2}}

\newcommand{\heterodownbox}[2]{\mathsf{sub{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterodownlayer}[2]{\mathsf{sub{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterodowncube}[2]{\mathsf{sub{\heteroname}cube}_{#1}^{#2}}
\newcommand{\depdownboxtype}[2]{\mathsf{Subdepbox}_{#1}^{#2}}
\newcommand{\depdownlayertype}[2]{\mathsf{Subdeplayer}_{#1}^{#2}}
\newcommand{\depdowncubetype}[2]{\mathsf{Subdepcube}_{#1}^{#2}}
\newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1}^{#2}}
\newcommand{\downlayertype}[2]{\mathsf{Sublayer}_{#1}^{#2}}
\newcommand{\downcubetype}[2]{\mathsf{Subcube}_{#1}^{#2}}
\newcommand{\cohreflbox}[1]{\mathsf{cohreflbox}_{#1}}
\newcommand{\cohrefllayer}[1]{\mathsf{cohrefllayer}_{#1}}
\newcommand{\cohreflcube}[1]{\mathsf{cohreflcube}_{#1}}
\newcommand{\cohrefleqbox}[1]{\mathsf{cohrefleqbox}_{#1}}
\newcommand{\cohrefleqlayer}[1]{\mathsf{cohrefleqlayer}_{#1}}
\newcommand{\cohrefleqcube}[1]{\mathsf{cohrefleqcube}_{#1}}
\newcommand{\cohboxtype}[2]{\mathsf{Cohbox}_{#1}^{#2}}
\newcommand{\cohlayertype}[2]{\mathsf{Cohlayer}_{#1}^{#2}}
\newcommand{\cohcubetype}[2]{\mathsf{Cohcube}_{#1}^{#2}}
\newcommand{\heterocohbox}[2]{\mathsf{coh{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterocohlayer}[2]{\mathsf{coh{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterocohcube}[2]{\mathsf{coh{\heteroname}cube}_{#1}^{#2}}
\newcommand{\myappdepbox}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdeplayer}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcube}[1]{\mathsf{homoappcube}_{#1}}
\newcommand{\myappdepfullcube}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myappdepboxtype}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdepfullboxtype}[1]{\mathsf{homoappfullbox}_{#1}}
\newcommand{\myappdeplayertype}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcubetype}[1]{\mathsf{homoappcube}_{#1}}
\newcommand{\myappdepfullcubetype}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myfullcube}[1]{\mathsf{fullcube}_{#1}}
\newcommand{\myfullheteroboxtype}[2]{\mathsf{fullBox}_{#1}^{#2}}
\newcommand{\myfullheterobox}[2]{\mathsf{full{\heteroname}box}_{#1}^{#2}}
\newcommand{\reflfullcube}[1]{\mathsf{reflfullcube}_{#1}}
\newcommand{\unitpoint}{\star}
\newcommand{\reflett}{\mathsf{refl}_{\mathit{ETT}}}
\newcommand{\mygpd}{\mathsf{gpd}}

\newcommand{\mycubset}[1]{\mathsf{cubset}_{#1}}
\newcommand{\mycubsetfrom}[2]{\mathsf{cubset}_{#1}^{\geq#2}}
\newcommand{\mydepcubset}[1]{\mathsf{dephomocubset}_{#1}}
\newcommand{\mydepcubsetfrom}[2]{\mathsf{dephomocubset}_{#1}^{\geq#2}}
\newcommand{\mydepcubsetcomp}[2]{\mathsf{dephomocubset}_{#1}^{=#2}}
\newcommand{\deppartialcubset}[2]{\mathsf{dephomocubset}_{#1}^{<#2}}
\newcommand{\properheterocubetype}[2]{\mathsf{Filler}_{#1}^{#2}}

\newcommand{\mydepheterocubset}[2]{\mathsf{depcubset}_{#1}^{#2}}
\newcommand{\mydepheterocubsetfrom}[3]{\mathsf{depcubset}_{#1}^{#2,\geq#3}}
\newcommand{\mydepheterocubsetcomp}[3]{\mathsf{depcubset}_{#1}^{#2,=#3}}
\newcommand{\deppartialheterocubset}[3]{\mathsf{depcubset}_{#1}^{#2,<#3}}
\newcommand{\myappheterodepbox}[1]{\mathsf{appbox}_{#1}}
\newcommand{\myappheterodeplayer}[1]{\mathsf{applayer}_{#1}}
\newcommand{\myappheterodepcube}[1]{\mathsf{appcube}_{#1}}
\newcommand{\myappheterodepfullcube}[1]{\mathsf{appfullcube}_{#1}}
\newcommand{\myappheterodepboxtype}[1]{\mathsf{appbox}_{#1}}
\newcommand{\myappheterodepfullboxtype}[3]{\mathsf{appfullbox}_{#1}^{#2,#3}}
\newcommand{\myappheterodeplayertype}[1]{\mathsf{applayer}_{#1}}
\newcommand{\myappheterodepcubetype}[1]{\mathsf{appcube}_{#1}}
\newcommand{\myappheterodepfullcubetype}[1]{\mathsf{appfullcube}_{#1}}

>>>>

\documentclass[10pt]{amsart}

\usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
\usepackage{bookmark, titling, fontspec, xargs, multirow, polyglossia, luacode, amssymb, listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace, makecell}
\usepackage[margin=0.3in]{geometry}

@@

@@

% The unit type
\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
\newcommand{\unitpoint}{\ensuremath{\star}}

% Definitional and extensional equality
\newcommand{\defeq}{\ensuremath{\triangleq}}
\newcommand{\eqett}{\ensuremath{\equiv_{\mathit{ETT}}}}
\newcommand{\reflett}{\ensuremath{\mathsf{refl}_{\mathit{ETT}}}}

% Box, layer, and cube
\newcommand{\mycubset}[1]{\ensuremath{\mathsf{cubset}_{#1}}}
\newcommand{\mybox}[2]{\ensuremath{\mathsf{box}_{#1}^{#2}}}
\newcommand{\mylayer}[2]{\ensuremath{\mathsf{layer}_{#1}^{#2}}}
\newcommand{\mycube}[2]{\ensuremath{\mathsf{cube}_{#1}^{#2}}}

@@

% Partials and fulls, related to box, cube, and tube
\newcommand{\border}[1]{\ensuremath{\mathsf{border}_{#1}}}
\newcommand{\partialcubset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
\newcommand{\mycubsetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}
\newcommand{\fulldownbox}[2]{\ensuremath{\mathsf{subfullbox}_{#1}^{#2}}}
\newcommand{\fulldowncube}[2]{\ensuremath{\mathsf{subfullcube}_{#1}^{#2}}}
\newcommand{\propercube}[1]{\ensuremath{\mathsf{properfiller}_{#1}}}
\newcommand{\mygroundedcube}[1]{\ensuremath{\mathsf{groundedcube}_{#1}}}
\newcommand{\tube}[1]{\ensuremath{\mathsf{tube}_{#1}}}
\newcommand{\mycubsetfrom}[2]{\ensuremath{\mathsf{cubset}_{#1}^{\geq#2}}}
\newcommand{\myfullcube}[1]{\ensuremath{\mathsf{fullcube}_{#1}}}

@@
